---
title: "Class11"
date: "2026-09-30"
output: 
  html_document:
    toc: TRUE 
    toc_float: TRUE
    numbered_sections: TRUE 
    code_dowloading: TRUE 
    code_folding: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning Objectives for Today 

-Scrape multiple we pages using 'for' loops

-Scrape multiple webapges using toe 'purrr::map()' type functions 


## Extending the course Bulletin scrape for multiple departments

for the sake of the example let us scrape the following pages:

[ISA]https://bulletin.miamioh.edu/courses-instruction/isa/
[MKT]https://bulletin.miamioh.edu/courses-instruction/mkt/

Note that if you are doing it for just a few departments, you can just repeat yur code a few times: however this is bad practice so we will not do it in class. Software engineers tend to refer to this as: **DRY**( no not repeat yourself).


```{r}
dept_abbr=c('acc','bus','isa','mkt') # extending example to 4 depts
# Line below shows how URL can be constructed by pasting0 (i.e., no space) the base)url, and the forward slash



courses_df=data.frame() #initialize the container
for (dept_name in dept_abbr){
  cat(rep("-",25))
  print(dept_name)
  dept_url = paste0(
    "https://bulletin.miamioh.edu/courses-instruction/", dept_name,"/")
  
  
  # for the titles I will use the selecor gadget and for the descriptions i will use the inspector ( to show alternative CSS selectors for what we did on Mon)
  
  webpage= rvest::read_html(dept_url)
  
  webpage |> rvest::html_elements("strong") |>  rvest::html_text2()-> titles
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs> div > p.courseblockdesc") |> 
    rvest::html_text2() -> descs
  
  df=data.frame(title=titles,desc=descs)
  df$title[1] |>  print() #showing only the first course title 
  
  courses_df=rbind(courses_df,df)
  cat(rep("-",25))
  
  }

```


# Re-examining the prior example with the 'purrr' package

My preffered approach with the purrr function is to first create my own function and then use it within the package

```{r}
scrape_mu_bulletin= function(dept_url) {
 
  webpage= rvest::read_html(dept_url)
  
  webpage |> rvest::html_elements("strong") |>  rvest::html_text2()-> titles
  webpage |> 
    rvest::html_elements("#sc_sccoursedescs> div > p.courseblockdesc") |> 
    rvest::html_text2() -> descs
  
  df=data.frame(title=titles,desc=descs)
  
  return(df)
}

test = scrape_mu_bulletin("https://bulletin.miamioh.edu/courses-instruction/bus/")

dept_abbr=c('acc','bus','isa','mkt')
my_urls=paste0(
  "https://bulletin.miamioh.edu/courses-instruction/",
  dept_abbr, "/"
)


# the map functions take son or more inputs(depending on thr function you are using)
# in this example, we only have 1 input for our function
#so we used map_() instead of map2_() [ 2 is if you have two inputs], p_map() [for three or more inputs]
#.x = the vector you are uterating over

courses_df_from_purrr=purrr::map_df(.x=my_urls,.f=scrape_mu_bulletin)

```












